The five axes of the Turtle: symmetry and asymmetry in NGC~6210

### 2020-12-07 latexdiff/ms-v2-expand.tex
Do latexdiff to get highlighted changes

\begin{figure}
\centering
\includegraphics[width=\linewidth]{figs/turtle-overview}
\caption{
  Images from the \textit{HST} WFPC2 camera of NGC~6210.
  (a)~A logarithmic stretch and an edge-detection algorithm are applied to an  \oiii{} \Wav{5007} image,
  in order to accentuate small-scale structure and remove large-scale radial brightness gradients.
  The most salient nebular features are labeled for reference.
  (b)~Same, but for \nii{} \Wav{6583}.
  (c)~Two-color composite image of \oii{} \Wav{3727} (red) and \oiii{} \Wav{5007} (green).
  Image credit: Robert Rubin and Christopher Ortiz (NASA/ESA Ames Research Center), Patrick Harrington and Nancy Jo Lame (University of Maryland), Reginald Dufour (Rice University), and NASA/ESA.
  (d)~Three-color composite image of \nii{} \Wav{6583} (red), broad \(V\) band (green), and \oiii{} \Wav{5007} (blue). Image credit: ESA/Hubble and NASA.}
\label{fig:hst}
\end{figure}

@@

\section{Longslit Spectroscopy}
\label{sec:observations}
 \begin{figure}
   \centering
   \includegraphics[width=0.38\textwidth]{figs/turtle-slits}
   \caption{
     Spectrograph slit positions for vertical orientations (upper panel),
     horizontal orientations (middle panel),
     and diagonal orientations (lower panel).
     Background image in each case is an \textit{HST} \oiii{} image of the nebula.
     In the top panel, slit positions from the 2015 season are indicated as solid lines
     and positions from other seasons are shown as dashed lines (see Table~\ref{table:pa5} for details). 
   }
  \label{fig:slit-positions}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.95\textwidth]{tere-figs/Figure3}
  \caption{Position--velocity line profiles for the slit positions from the 2015 run are shown in sets where
the H$\alpha$ bi-dimensional line profile is on the left panel of the set, the \oiii{} line profile is on the central panel 
and the \nii{} line profile is on the right panel. The corresponding slit positions are indicated at the top of
each set of line profiles. The velocity scale is heliocentric and the spatial scale is indicated in arcsec 
with respect to the central star.}
  \label{fig:pv-array}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-1d-line-profiles}
  \caption{
    Thick colored lines show one-dimensional extracted velocity profiles
    of (top to bottom) \nii{} (red), \Ha{} (purple) and \oiii{} (light blue)
    for a  short section of slit~e
    (length \SI{2}{arcsec},
    centered \SI{3}{arcsec} north of the central star).
    For the \nii{} and \oiii{} lines, four-gaussian fits are shown
    (continuous thin black lines show the individual components,
    while thin dashed line shows the total profile).
    The bottom panel shows the residuals of these fits on an expanded scale.
    Short vertical colored lines mark the centroid velocity of each of the four components,
    with thicker lines corresponding to the high-ionization shell
    and thinner lines low-ionization knot complexes.
    The vertical dashed line shows the systemic velocity.
    No fits are performed to the \Ha{} line
    because the larger thermal broadening means that
    the four components cannot be reliably separated.
  }
  \label{fig:spec-1d}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-halo-slit-x}
  \caption{
    Deep images and spectra of the outer halo of NGC~6210, showing knotty structure.
    (a)~Composite mosaic of \oiii{} images,
    each with an exposure time of 1800~s,
    giving a combined field of view of \(3' \times 3'\) centered on the nebula.
    The position of slit~x is shown, for which a deep \Ha{} spectrum was obtained.
    Note that different sections of the mosaic are shown with different brightness normalizations,
    leading to abrupt jumps at the boundaries.
    The images were taken with an occulting bar that blocks out the bright core of the nebula,
    allowing the faint halo to be seen.
    (b)~\Ha{} spectrum from slit~x, showing emission from two of the halo knots.
    The red dotted line shows the nebular nominal systemic velocity.
  }
  \label{fig:halo-knots}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/oiii-propermotions-lores}
  \caption{Proper motions derived from two HST \oiii{} images (F502N
    filter) separated by 10.45 years, using the FLCT algorithm with a
    Gaussian window width of 10~pixels. The key at bottom left shows a
    proper motion of \SI{10}{mas.yr^{-1}}, corresponding to
    \SI{95}{km.s^{-1}} for an assumed distance of \SI{2}{kpc}.}
  \label{fig:proper-motions-oiii}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/nii-propermotions-lores}
  \caption{As Fig.~\ref{fig:proper-motions-oiii} but for two HST
    \nii{} images (F658N filter). Note that the field of view is
    cropped slightly smaller than for \oiii{}.}
  \label{fig:proper-motions-nii}
\end{figure}

\begin{figure*}
  \centering
  % \includegraphics[width=\linewidth]{figs/turtle-peanut-map-lores}
  \includegraphics[width=\linewidth]{figs/turtle-peanut-map}
  \caption{
    Velocity features in the high-ionization shells,
    which have been identified in the \oiii{} slits.
    (a)~Blue-shifted features. 
    (b)~Red-shifted features.
    Each are labelled with their line-of-sight velocity
    with respect to the nominal systemic velocity of \SI{-40}{km.s^{-1}}.
    Solid lines show features in the inner shell,
    dashed lines show features in the intermediate shell,
    and dot-dashed lines show miscellaneous features between the two shells.
    The line width is a qualitative indicator of the brightness of each feature.
    The background grayscale shows a high-pass filtered version of the HST \oiii{} image.
    The star symbol in this and subsequent figures indicates the position of the central star.
  }
  \label{fig:shell-velocity-components}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-heii-shell-components}
  \caption{
    Velocity features in the highest-ionization gas,
    which have been identified in the \heii{} slits.
    (a)~Blue-shifted features. (b)~Red-shifted features.
    Each are labelled with their line-of-sight velocity
    with respect to the nominal systemic velocity of \SI{-40}{km.s^{-1}}.
    The line width is a qualitative indicator of the brightness of each feature,
    with dashed lines showing the very faintest features.
    The background grayscale image is the same as in Fig.~\ref{fig:shell-velocity-components}.
  }
  \label{fig:heii-shell-components}
\end{figure*}

\begin{figure*}
  \centering
  % \includegraphics[width=\linewidth]{figs/turtle-knot-complex-map-lores}
  \includegraphics[width=\linewidth]{figs/turtle-knot-complex-map}
  \caption{
    Velocity features in the low-ionization knot complexes,
    which have been identified in the \nii{} slits.
    (a)~Blue-shifted features.
    (b)~Red-shifted features.
    Each is labelled with their line-of-sight velocity
    with respect to the nominal systemic velocity of \SI{-40}{km.s^{-1}}.
    The line width is a qualitative indicator of the brightness of each feature.
  }
  \label{fig:knot-complex-map}
% \end{figure*}

@@

\begin{figure}
  \centering
  % \includegraphics[width=\linewidth]{figs/turtle-halo-map-lores}
  \includegraphics[width=\linewidth]{figs/turtle-halo-map}
  \caption{
    Velocity components in the halo, all measured from the \oiii{} spectra with slit positions as indicated.
    Components are divided into three classes:
    inner halo (pink ellipses), outer halo (yellow ellipses),
    and halo knots (green ellipses).
    The inner portion of the background image is
    the same high-pass-filtered \textit{HST} image
    shown in Figs.~\ref{fig:shell-velocity-components} and~\ref{fig:outer-lobe-components}.
    The outer portion of the background image is a deep \oiii{} exposure of the halo
    obtained with MES-SPM in direct imaging mode with an occulting bar (see Fig.~\ref{fig:halo-knots}).
  }
  \label{fig:halo-components}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-shell-velocity-axes-annotated}
  \caption{
    Radial velocity versus position
    for the shell features shown in Fig.~\ref{fig:shell-velocity-components}.
    Results are shown along two axes:
    Axis~A (upper panel) is the apparent projected major axis of the inner shell,
    while Axis~B (lower panel) is perpendicular to this.
    Large blue circles show the inner shell,
    small red circles show the intermediate shell,
    and green triangles show miscellaneous features between the two shells.
    Darker colors indicate features that are closer to each respective axis.
    Colored lines are merely to guide the eye,
    and show possible interpretations of the shell kinematics along the two axes.
  }
  \label{fig:shell-velocity-axes}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-heii-shell-annotated}
  \caption{
    Reconstructed velocity channel maps from the \heii{} slit spectra,
    showing the highest ionization gas in the nebula.
    The color image is constructed from 3 channels, each of width \SI{20}{km.s^{-1}},
    as indicated in the figure.  Contours show the \oiii{} HST image.
    No spatial interpolation is performed, so regions between the slits are lacking data,
    indicated by olive green color.
  }
  \label{fig:heii-shell-annotated}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-heii-shell-velocity-axes-annotated}
  \caption{
    Radial velocity versus position
    for the \heii{} shell features shown in Fig.~\ref{fig:heii-shell-components}.
    Results are shown projected along the same two axes
    as in Fig.~\ref{fig:shell-velocity-axes}:
    Axis~A (upper panel) and Axis~B (lower panel).
    Colored lines show the \oiii{} shells from Fig.~\ref{fig:shell-velocity-axes}.  
  }
  \label{fig:heii-shell-velocity-axes}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-nii-knot-complexes}
  \caption{
    Reconstructed velocity channel maps from the \nii{} slit spectra,
    showing the blue-shifted (left panel) and red-shifted (right panel) knot complexes.
    Note that channel maps have not been spatially interpolated,
    so that the individual slit positions can be seen.
    Each color image is constructed from 3 channels, each of width \SI{20}{km.s^{-1}},
    as indicated on the figure.
    All velocities are with respect to the nominal heliocentric systemic velocity of \SI{-40}{km.s^{-1}}.
    The low-ionization emission components from Fig.~\ref{fig:knot-complex-map}
    have been classified into 6 knot complexes,
    which are shown as colored outlines.
    Regions that lack data are shown in dark turquoise (left panel) and olive green (right panel).
  }
  \label{fig:knot-complexes}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-knot-complexes-velocity-axes-annotated}
  \caption{
    Radial velocity versus position
    for the low-ionization features shown in Fig.~\ref{fig:knot-complex-map}.
    Results are shown projected along the same two axes,
    Axis~A (upper panel) and Axis~B (lower panel),
    as in Fig.~\ref{fig:shell-velocity-axes},
    but this time each feature is shown projected along both axes.
    The features are divided into different knot complexes,
    as shown in Fig.~\ref{fig:knot-complexes},
    which are indicated by symbol type and color.
    Symbol size is proportional to feature brightness (log scale)
    and symbol shade indicates position along the other axis (darker is more positive).
    Continuous lines show the same high ionization shells
    as in Fig.~\ref{fig:shell-velocity-axes}.
  }
  \label{fig:knot-complex-velocity-axes}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-inclination-histogram}
  \caption{Distribution of outflow inclinations with respect to the plane of the sky for the different features.}
  \label{fig:inclinations}
\end{figure}

@@

\subsection{Comparison with post-AGB stellar evolution tracks}
\label{sec:comparison-with-post}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/hr-pne-annotated}
  \caption{
    HR diagram of planetary nebula central stars,
    showing the observed luminosity and effective temperature of the Turtle
    (large star symbol),
    compared with post-AGB evolutionary tracks from
    \citet{Miller-Bertolami:2016a}
    (solid lines, labelled with initial stellar mass in solar masses).
    Small star symbols show an evolutionary time along each track equal
    to the kinematic age of the intermediate shell of NGC~6210,
    with purple shading indicating 50\% variation about this value.
    Open triangle symbols show sources from \citet{Bear:2017a}
    that are suspected to harbor triple star systems on the basis of the nebular morphology.
    Filled symbols shows the sample of ``young-adult'' nebulae
    that have been selected to be physically similar to NGC~6210
    and which are illustrated in Figure~\ref{fig:cousins}.
    Symbol shape indicates the morphological complexity, from simple (circle) to multipolar (cross).
  }
  \label{fig:hr-diagram}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/cousins-of-the-turtle-lores}
  \caption{
    A selection of planetary nebulae that are similar to NGC~6210
    in terms of central star effective temperature and atmospheric abundances,
    as well as nebular radius, luminosity and ionizing optical depth.
    All nebulae are shown at the same physical scale (see scale bar of \SI{0.2}{pc}).
    Each row corresponds to a different Peimbert type, from bottom to top:
    Type~III, Type~IIb, Type~IIa,
    in decreasing order of stellar population age
    and increasing order of stellar mass.
    Within each row, the nebulae are arranged from left to right
    in order of increasing geometric complexity.
    Image credits: Judy Schmidt/HST for all except
    NGC~1535 (Mount Lemmon SkyCenter, University of Arizona)
    and outer portions of NGC~6309 \citep{Rubio:2015a}.
  }
  \label{fig:cousins}
\end{figure*}

@@

\bibliography{turtle-paper-refs}
\appendix

>>>>

\begin{figure}
\centering
% inside_import 
% before 
% ignored 
% args width=\linewidth
% full_filename figs/turtle-overview
% after 
\includegraphics[width=\linewidth]{figs/turtle-overview}
\caption{
  Images from the \textit{HST} WFPC2 camera of NGC~6210.
  (a)~A logarithmic stretch and an edge-detection algorithm are applied to an  \oiii{} \Wav{5007} image,
  in order to accentuate small-scale structure and remove large-scale radial brightness gradients.
  The most salient nebular features are labeled for reference.
  (b)~Same, but for \nii{} \Wav{6583}.
  (c)~Two-color composite image of \oii{} \Wav{3727} (red) and \oiii{} \Wav{5007} (green).
  Image credit: Robert Rubin and Christopher Ortiz (NASA/ESA Ames Research Center), Patrick Harrington and Nancy Jo Lame (University of Maryland), Reginald Dufour (Rice University), and NASA/ESA.
  (d)~Three-color composite image of \nii{} \Wav{6583} (red), broad \(V\) band (green), and \oiii{} \Wav{5007} (blue). Image credit: ESA/Hubble and NASA.}
\label{fig:hst}
\end{figure}

@@

\section{Longslit Spectroscopy}
\label{sec:observations}
 \begin{figure}
   \centering
% inside_import 
% before    
% ignored  
% args width=0.38\textwidth
% full_filename figs/turtle-slits
% after 
   \includegraphics[width=0.38\textwidth]{figs/turtle-slits}
   \caption{
     Spectrograph slit positions for vertical orientations (upper panel),
     horizontal orientations (middle panel),
     and diagonal orientations (lower panel).
     Background image in each case is an \textit{HST} \oiii{} image of the nebula.
     In the top panel, slit positions from the 2015 season are indicated as solid lines
     and positions from other seasons are shown as dashed lines (see Table~\ref{table:pa5} for details). 
   }
  \label{fig:slit-positions}
\end{figure}

@@

\begin{figure*}
  \centering
% inside_import 
% before   
% ignored  
% args width=0.95\textwidth
% full_filename tere-figs/Figure3
% after 
  \includegraphics[width=0.95\textwidth]{tere-figs/Figure3}
  \caption{Position--velocity line profiles for the slit positions from the 2015 run are shown in sets where
the H$\alpha$ bi-dimensional line profile is on the left panel of the set, the \oiii{} line profile is on the central panel 
and the \nii{} line profile is on the right panel. The corresponding slit positions are indicated at the top of
each set of line profiles. The velocity scale is heliocentric and the spatial scale is indicated in arcsec 
with respect to the central star.}
  \label{fig:pv-array}
\end{figure*}

\begin{figure}
  \centering
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/turtle-1d-line-profiles
% after 
  \includegraphics[width=\linewidth]{figs/turtle-1d-line-profiles}
  \caption{
    Thick colored lines show one-dimensional extracted velocity profiles
    of (top to bottom) \nii{} (red), \Ha{} (purple) and \oiii{} (light blue)
    for a  short section of slit~e
    (length \SI{2}{arcsec},
    centered \SI{3}{arcsec} north of the central star).
    For the \nii{} and \oiii{} lines, four-gaussian fits are shown
    (continuous thin black lines show the individual components,
    while thin dashed line shows the total profile).
    The bottom panel shows the residuals of these fits on an expanded scale.
    Short vertical colored lines mark the centroid velocity of each of the four components,
    with thicker lines corresponding to the high-ionization shell
    and thinner lines low-ionization knot complexes.
    The vertical dashed line shows the systemic velocity.
    No fits are performed to the \Ha{} line
    because the larger thermal broadening means that
    the four components cannot be reliably separated.
  }
  \label{fig:spec-1d}
\end{figure}

\begin{figure}
  \centering
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/turtle-halo-slit-x
% after 
  \includegraphics[width=\linewidth]{figs/turtle-halo-slit-x}
  \caption{
    Deep images and spectra of the outer halo of NGC~6210, showing knotty structure.
    (a)~Composite mosaic of \oiii{} images,
    each with an exposure time of 1800~s,
    giving a combined field of view of \(3' \times 3'\) centered on the nebula.
    The position of slit~x is shown, for which a deep \Ha{} spectrum was obtained.
    Note that different sections of the mosaic are shown with different brightness normalizations,
    leading to abrupt jumps at the boundaries.
    The images were taken with an occulting bar that blocks out the bright core of the nebula,
    allowing the faint halo to be seen.
    (b)~\Ha{} spectrum from slit~x, showing emission from two of the halo knots.
    The red dotted line shows the nebular nominal systemic velocity.
  }
  \label{fig:halo-knots}
\end{figure}

@@

\begin{figure}
  \centering
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/oiii-propermotions-lores
% after 
  \includegraphics[width=\linewidth]{figs/oiii-propermotions-lores}
  \caption{Proper motions derived from two HST \oiii{} images (F502N
    filter) separated by 10.45 years, using the FLCT algorithm with a
    Gaussian window width of 10~pixels. The key at bottom left shows a
    proper motion of \SI{10}{mas.yr^{-1}}, corresponding to
    \SI{95}{km.s^{-1}} for an assumed distance of \SI{2}{kpc}.}
  \label{fig:proper-motions-oiii}
\end{figure}

\begin{figure}
  \centering
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/nii-propermotions-lores
% after 
  \includegraphics[width=\linewidth]{figs/nii-propermotions-lores}
  \caption{As Fig.~\ref{fig:proper-motions-oiii} but for two HST
    \nii{} images (F658N filter). Note that the field of view is
    cropped slightly smaller than for \oiii{}.}
  \label{fig:proper-motions-nii}
\end{figure}

\begin{figure*}
  \centering
  % \includegraphics[width=\linewidth]{figs/turtle-peanut-map-lores}
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/turtle-peanut-map
% after 
  \includegraphics[width=\linewidth]{figs/turtle-peanut-map}
  \caption{
    Velocity features in the high-ionization shells,
    which have been identified in the \oiii{} slits.
    (a)~Blue-shifted features. 
    (b)~Red-shifted features.
    Each are labelled with their line-of-sight velocity
    with respect to the nominal systemic velocity of \SI{-40}{km.s^{-1}}.
    Solid lines show features in the inner shell,
    dashed lines show features in the intermediate shell,
    and dot-dashed lines show miscellaneous features between the two shells.
    The line width is a qualitative indicator of the brightness of each feature.
    The background grayscale shows a high-pass filtered version of the HST \oiii{} image.
    The star symbol in this and subsequent figures indicates the position of the central star.
  }
  \label{fig:shell-velocity-components}
\end{figure*}

\begin{figure*}
  \centering
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/turtle-heii-shell-components
% after 
  \includegraphics[width=\linewidth]{figs/turtle-heii-shell-components}
  \caption{
    Velocity features in the highest-ionization gas,
    which have been identified in the \heii{} slits.
    (a)~Blue-shifted features. (b)~Red-shifted features.
    Each are labelled with their line-of-sight velocity
    with respect to the nominal systemic velocity of \SI{-40}{km.s^{-1}}.
    The line width is a qualitative indicator of the brightness of each feature,
    with dashed lines showing the very faintest features.
    The background grayscale image is the same as in Fig.~\ref{fig:shell-velocity-components}.
  }
  \label{fig:heii-shell-components}
\end{figure*}

\begin{figure*}
  \centering
  % \includegraphics[width=\linewidth]{figs/turtle-knot-complex-map-lores}
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/turtle-knot-complex-map
% after 
  \includegraphics[width=\linewidth]{figs/turtle-knot-complex-map}
  \caption{
    Velocity features in the low-ionization knot complexes,
    which have been identified in the \nii{} slits.
    (a)~Blue-shifted features.
    (b)~Red-shifted features.
    Each is labelled with their line-of-sight velocity
    with respect to the nominal systemic velocity of \SI{-40}{km.s^{-1}}.
    The line width is a qualitative indicator of the brightness of each feature.
  }
  \label{fig:knot-complex-map}
% \end{figure*}

@@

\begin{figure}
  \centering
  % \includegraphics[width=\linewidth]{figs/turtle-halo-map-lores}
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/turtle-halo-map
% after 
  \includegraphics[width=\linewidth]{figs/turtle-halo-map}
  \caption{
    Velocity components in the halo, all measured from the \oiii{} spectra with slit positions as indicated.
    Components are divided into three classes:
    inner halo (pink ellipses), outer halo (yellow ellipses),
    and halo knots (green ellipses).
    The inner portion of the background image is
    the same high-pass-filtered \textit{HST} image
    shown in Figs.~\ref{fig:shell-velocity-components} and~\ref{fig:outer-lobe-components}.
    The outer portion of the background image is a deep \oiii{} exposure of the halo
    obtained with MES-SPM in direct imaging mode with an occulting bar (see Fig.~\ref{fig:halo-knots}).
  }
  \label{fig:halo-components}
\end{figure}

\begin{figure}
  \centering
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/turtle-shell-velocity-axes-annotated
% after 
  \includegraphics[width=\linewidth]{figs/turtle-shell-velocity-axes-annotated}
  \caption{
    Radial velocity versus position
    for the shell features shown in Fig.~\ref{fig:shell-velocity-components}.
    Results are shown along two axes:
    Axis~A (upper panel) is the apparent projected major axis of the inner shell,
    while Axis~B (lower panel) is perpendicular to this.
    Large blue circles show the inner shell,
    small red circles show the intermediate shell,
    and green triangles show miscellaneous features between the two shells.
    Darker colors indicate features that are closer to each respective axis.
    Colored lines are merely to guide the eye,
    and show possible interpretations of the shell kinematics along the two axes.
  }
  \label{fig:shell-velocity-axes}
\end{figure}

@@

\begin{figure}
  \centering
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/turtle-heii-shell-annotated
% after 
  \includegraphics[width=\linewidth]{figs/turtle-heii-shell-annotated}
  \caption{
    Reconstructed velocity channel maps from the \heii{} slit spectra,
    showing the highest ionization gas in the nebula.
    The color image is constructed from 3 channels, each of width \SI{20}{km.s^{-1}},
    as indicated in the figure.  Contours show the \oiii{} HST image.
    No spatial interpolation is performed, so regions between the slits are lacking data,
    indicated by olive green color.
  }
  \label{fig:heii-shell-annotated}
\end{figure}

\begin{figure}
  \centering
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/turtle-heii-shell-velocity-axes-annotated
% after 
  \includegraphics[width=\linewidth]{figs/turtle-heii-shell-velocity-axes-annotated}
  \caption{
    Radial velocity versus position
    for the \heii{} shell features shown in Fig.~\ref{fig:heii-shell-components}.
    Results are shown projected along the same two axes
    as in Fig.~\ref{fig:shell-velocity-axes}:
    Axis~A (upper panel) and Axis~B (lower panel).
    Colored lines show the \oiii{} shells from Fig.~\ref{fig:shell-velocity-axes}.  
  }
  \label{fig:heii-shell-velocity-axes}
\end{figure}

@@

\begin{figure*}
  \centering
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/turtle-nii-knot-complexes
% after 
  \includegraphics[width=\linewidth]{figs/turtle-nii-knot-complexes}
  \caption{
    Reconstructed velocity channel maps from the \nii{} slit spectra,
    showing the blue-shifted (left panel) and red-shifted (right panel) knot complexes.
    Note that channel maps have not been spatially interpolated,
    so that the individual slit positions can be seen.
    Each color image is constructed from 3 channels, each of width \SI{20}{km.s^{-1}},
    as indicated on the figure.
    All velocities are with respect to the nominal heliocentric systemic velocity of \SI{-40}{km.s^{-1}}.
    The low-ionization emission components from Fig.~\ref{fig:knot-complex-map}
    have been classified into 6 knot complexes,
    which are shown as colored outlines.
    Regions that lack data are shown in dark turquoise (left panel) and olive green (right panel).
  }
  \label{fig:knot-complexes}
\end{figure*}

\begin{figure}
  \centering
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/turtle-knot-complexes-velocity-axes-annotated
% after 
  \includegraphics[width=\linewidth]{figs/turtle-knot-complexes-velocity-axes-annotated}
  \caption{
    Radial velocity versus position
    for the low-ionization features shown in Fig.~\ref{fig:knot-complex-map}.
    Results are shown projected along the same two axes,
    Axis~A (upper panel) and Axis~B (lower panel),
    as in Fig.~\ref{fig:shell-velocity-axes},
    but this time each feature is shown projected along both axes.
    The features are divided into different knot complexes,
    as shown in Fig.~\ref{fig:knot-complexes},
    which are indicated by symbol type and color.
    Symbol size is proportional to feature brightness (log scale)
    and symbol shade indicates position along the other axis (darker is more positive).
    Continuous lines show the same high ionization shells
    as in Fig.~\ref{fig:shell-velocity-axes}.
  }
  \label{fig:knot-complex-velocity-axes}
\end{figure}

@@

\begin{figure}
  \centering
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/turtle-inclination-histogram
% after 
  \includegraphics[width=\linewidth]{figs/turtle-inclination-histogram}
  \caption{Distribution of outflow inclinations with respect to the plane of the sky for the different features.}
  \label{fig:inclinations}
\end{figure}

@@

\subsection{Comparison with post-AGB stellar evolution tracks}
\label{sec:comparison-with-post}
\begin{figure}
  \centering
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/hr-pne-annotated
% after 
  \includegraphics[width=\linewidth]{figs/hr-pne-annotated}
  \caption{
    HR diagram of planetary nebula central stars,
    showing the observed luminosity and effective temperature of the Turtle
    (large star symbol),
    compared with post-AGB evolutionary tracks from
    \citet{Miller-Bertolami:2016a}
    (solid lines, labelled with initial stellar mass in solar masses).
    Small star symbols show an evolutionary time along each track equal
    to the kinematic age of the intermediate shell of NGC~6210,
    with purple shading indicating 50\% variation about this value.
    Open triangle symbols show sources from \citet{Bear:2017a}
    that are suspected to harbor triple star systems on the basis of the nebular morphology.
    Filled symbols shows the sample of ``young-adult'' nebulae
    that have been selected to be physically similar to NGC~6210
    and which are illustrated in Figure~\ref{fig:cousins}.
    Symbol shape indicates the morphological complexity, from simple (circle) to multipolar (cross).
  }
  \label{fig:hr-diagram}
\end{figure}

@@

\begin{figure*}
  \centering
% inside_import 
% before   
% ignored  
% args width=\linewidth
% full_filename figs/cousins-of-the-turtle-lores
% after 
  \includegraphics[width=\linewidth]{figs/cousins-of-the-turtle-lores}
  \caption{
    A selection of planetary nebulae that are similar to NGC~6210
    in terms of central star effective temperature and atmospheric abundances,
    as well as nebular radius, luminosity and ionizing optical depth.
    All nebulae are shown at the same physical scale (see scale bar of \SI{0.2}{pc}).
    Each row corresponds to a different Peimbert type, from bottom to top:
    Type~III, Type~IIb, Type~IIa,
    in decreasing order of stellar population age
    and increasing order of stellar mass.
    Within each row, the nebulae are arranged from left to right
    in order of increasing geometric complexity.
    Image credits: Judy Schmidt/HST for all except
    NGC~1535 (Mount Lemmon SkyCenter, University of Arizona)
    and outer portions of NGC~6309 \citep{Rubio:2015a}.
  }
  \label{fig:cousins}
\end{figure*}

@@

\begin{thebibliography}{}
\makeatletter
\relax
\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
  {\mn@doi@[]}}
\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
  \endgroup}
\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
  {dblp:#1}}
\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}

\bibitem[\protect\citeauthoryear{{Ali}, {Sabin}, {Snaid}  \& {Basurah}}{{Ali}
  et~al.}{2012}]{Ali:2012a}
{Ali} A.,  {Sabin} L.,  {Snaid} S.,   {Basurah} H.~M.,  2012, \aap, 541, A98

\bibitem[\protect\citeauthoryear{{Balick}}{{Balick}}{1987}]{Balick:1987b}
{Balick} B.,  1987, \aj, 94, 671

\bibitem[\protect\citeauthoryear{{Balick} \& {Frank}}{{Balick} \&
  {Frank}}{2002}]{Balick:2002a}
{Balick} B.,  {Frank} A.,  2002, \araa, 40, 439

\bibitem[\protect\citeauthoryear{{Balick}, {Perinotto}, {Maccioni}, {Terzian}
  \& {Hajian}}{{Balick} et~al.}{1994}]{Balick:1994a}
{Balick} B.,  {Perinotto} M.,  {Maccioni} A.,  {Terzian} Y.,   {Hajian} A.,
  1994, \apj, 424, 800

\bibitem[\protect\citeauthoryear{{Barker}}{{Barker}}{1989}]{Barker:1989a}
{Barker} T.,  1989, \apj, 340, 921

\bibitem[\protect\citeauthoryear{{Bear} \& {Soker}}{{Bear} \&
  {Soker}}{2017}]{Bear:2017a}
{Bear} E.,  {Soker} N.,  2017, \apjl, 837, L10

\bibitem[\protect\citeauthoryear{{Becker}, {Gieseking}  \& {Solf}}{{Becker}
  et~al.}{1984}]{Becker:1984a}
{Becker} I.,  {Gieseking} F.,   {Solf} J.,  1984, Mitteilungen der
  Astronomischen Gesellschaft Hamburg, 62, 253

\bibitem[\protect\citeauthoryear{{Boffin} \& {Jones}}{{Boffin} \&
  {Jones}}{2019}]{Boffin:2019a}
{Boffin} H. M.~J.,  {Jones} D.,  2019, {The Importance of Binaries in the
  Formation and Evolution of Planetary Nebulae}.
Springer International Publishing, Switzerland

\bibitem[\protect\citeauthoryear{{Bohigas}, {Escalante}, {Rodr{\'{\i}}guez}  \&
  {Dufour}}{{Bohigas} et~al.}{2015}]{Bohigas:2015c}
{Bohigas} J.,  {Escalante} V.,  {Rodr{\'{\i}}guez} M.,   {Dufour} R.~J.,  2015,
  \mnras, 447, 817

\bibitem[\protect\citeauthoryear{{Cardelli}, {Clayton}  \& {Mathis}}{{Cardelli}
  et~al.}{1989}]{Cardelli:1989a}
{Cardelli} J.~A.,  {Clayton} G.~C.,   {Mathis} J.~S.,  1989, \apj, 345, 245

\bibitem[\protect\citeauthoryear{{Chen}, {Frank}, {Blackman}, {Nordhaus}  \&
  {Carroll-Nellenback}}{{Chen} et~al.}{2017}]{Chen:2017b}
{Chen} Z.,  {Frank} A.,  {Blackman} E.~G.,  {Nordhaus} J.,
  {Carroll-Nellenback} J.,  2017, \mnras, 468, 4465

\bibitem[\protect\citeauthoryear{{Chen}, {Ivanova}  \&
  {Carroll-Nellenback}}{{Chen} et~al.}{2020}]{Chen:2020a}
{Chen} Z.,  {Ivanova} N.,   {Carroll-Nellenback} J.,  2020, \apj, 892, 110

\bibitem[\protect\citeauthoryear{{Chong}, {Kwok}, {Imai}, {Tafoya}  \&
  {Chibueze}}{{Chong} et~al.}{2012}]{Chong:2012a}
{Chong} S.~N.,  {Kwok} S.,  {Imai} H.,  {Tafoya} D.,   {Chibueze} J.,  2012,
  \apj, 760, 115

\bibitem[\protect\citeauthoryear{{Corradi}, {Steffen}, {Schönberner}  \&
  {Jacob}}{{Corradi} et~al.}{2007}]{Corradi:2007a}
{Corradi} R.~L.~M.,  {Steffen} M.,  {Schönberner} D.,   {Jacob} R.,  2007,
  \aap, 474, 529

\bibitem[\protect\citeauthoryear{{Curtis}}{{Curtis}}{1918}]{Curtis:1918a}
{Curtis} H.~D.,  1918, Publications of Lick Observatory, 13, 55
